Probability Distribution Checks

### 2017-03-28 Probability_distribution_checks.Rmd
add probability plots for tiller sheath blight incidence

## 2015 Check probability distribution fit for tiller sheath blight

@@

@@

>>>>

## 2015 Check probability distribution fit for tiller sheath blight severity

@@

## 2015 Check probability distribution fit for tiller sheath blight incidence

f1 <- fitdist(AUDPS_2015$TShB_incidence_mean, "norm")
plot(f1)
qqp(AUDPS_2015$TShB_incidence_mean, "norm")

f2 <- fitdist(AUDPS_2015$TShB_incidence_mean, "exp")
plot(f2)
qqp(AUDPS_2015$TShB_incidence_mean, "exp")

@@

## 2016 Check probability distribution fit for tiller sheath blight incidence

f1 <- fitdist(AUDPS_2016$TShB_incidence_mean, "norm")
plot(f1)
qqp(AUDPS_2016$TShB_incidence_mean, "norm")

f2 <- fitdist(AUDPS_2016$TShB_incidence_mean, "exp")
plot(f2)
qqp(AUDPS_2016$TShB_incidence_mean, "exp")
